Quality Definitions of Qualities

### 2020-01-20 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated more definitions

\begin{defn}
	By verification, we mean all activities that are undertaken to ascertain that the
	software meets its objectives \citep{GhezziEtAl2003}.
\end{defn}
\noindent \textbf{Proposed Definition}

Definition~\ref{Defn_Verifiability1} rephrased:
Verifiability is the extent to which a set of tests can be written and executed, to demonstrate
that the delivered system meets each specified requirement.

@@

Definition is concise and measurable.  Verifiability involves solving the
equations right \citep[p.~23]{Roache1998}.

@@

\begin{defn} \label{Validatability_Selected} 
  Validation is the process of evaluating software during or at the end of the
  development process to determine whether it satisfies specified business
  requirements \citep{softwaretestingfundamentals}.  \wss{Please use the
  author's name for this citation.  If that isn't known, use the name of the
  organization that published this material.} \oo{This is a weblink, that's the organization's name I guess}
\end{defn}

@@

\begin{defn}
	Validation is concerned with establishing that the product fulfills its
	intended use \citep{Van vilet}.
\end{defn}

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
  \wss{This reference is not appearing in the Reference
  list.  We also don't really want a Wikipedia citation in a scholarly paper.
  Can you please find the source where this definition originally came from?}\oo{Could not find a different source from Wikipedia}
\end{defn}

@@

Definition~ \oo{need to discuss this quality, we might just define
  validatability from validation definitions above? Resources are limited for
  'validatability'}.

@@

\subsection{\notdone{Testability} \oo{owner}}

@@

@@

\begin{defn}
  Extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. \oo{Definition check pass}
\end{defn}

@@

\begin{defn}
  The ability of a system to perform its required functions under stated
  conditions whenever required—having a long mean time between failures
  \citep{mcconnell2004code}.
\end{defn}
\begin{defn} \label{reliabilitySelected2} Reliability can be estimated as ``the
  average time interval between two faliures, also called the mean time to
  faliure (MTTF). Clearly, MTTF (t) = 1/FI (t)''. Where FI (t) is the faliure
  intensity - the number of faliures per unit time \citep{GhezziEtAl2003}.
\end{defn}
\oo{Statistical definition from  \citep{GhezziEtAl2003} added}

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:
Probability of failure-free operation of a computer program in a specified
environment for a specified time, i.e. the average time interval between two
faliures also known as the mean time to failure (MTTF).

>>>>

\begin{defn}
	By verification, we mean all activities that are undertaken to ascertain that the
	software meets its objectives \citep{GhezziEtAl2003}.
\end{defn}

\begin{defn}
	 Verification is the process of evaluating a system or component to determine whether the products
	 of a given development phase satisfy the conditions imposed at the start of that phase \citep{IEEEStdGlossarySET1990}.
\end{defn}
\noindent \textbf{Proposed Definition}

Definition~\ref{Defn_Verifiability1} rephrased:
Verifiability is the extent to which a set of tests can be written and executed, to demonstrate
that the delivered system meets the specification.

@@

Definition is concise and measurable.  Verifiability involves solving the
equations right \citep[p.~23]{Roache1998} and the definition states that system needs to be verifiable based on the specifications..

@@

@@

\begin{defn}
	Validation is concerned with establishing that the product fulfills its
	intended use \citep{van2008software}.
\end{defn}

\begin{defn} \label{Defn_Validatability}
  The process of evaluating a system or component during or at the end of the
  development process to determine whether it satisfies specified requirements
  \citep{IEEEStdGlossarySET1990}.
\end{defn}

@@

Definition \ref{Defn_Validatability} rephrased:  The effort required in evaluating
a system or component during or at the end of the development process to determine
whether it satisfies specified requirements

@@

Definition describes that system should be measurable through the development life cycle,
It is concise and can be measured.
\subsection{\notdone{Testability} \oo{owner}}

@@

\begin{defn}
	Effort required to test a program to ensure it performs
	its intended function \citep{McCallEtAl1977}.
\end{defn}

\begin{defn} \label{Defn_Testability}
	 The degree to which a system or component facilitates the establishment of
	 test criteria and the performance of tests to determine whether those
	 criteria have been met \citep{IEEEStdGlossarySET1990}.
\end{defn}

Definition \ref{Defn_Testability}: The degree to which a system or component
 facilitates the establishment of test criteria and the performance of tests
 to determine whether those criteria have been met.

Definition is concise and measurable

@@

\begin{defn}
  Extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}.
\end{defn}

@@

\begin{defn}
  The ability of a system to perform its required functions under stated
  conditions whenever required—having a long mean time between failures
  \citep{mcconnell2004code}.
\end{defn}
\begin{defn} \label{reliabilitySelected2} Reliability can be estimated as ``the
  average time interval between two failures, also called the mean time to
  failure (MTTF). Clearly, MTTF (t) = 1/FI (t)''. Where FI (t) is the failure
  intensity - the number of failures per unit time \citep{GhezziEtAl2003}.
\end{defn}
\oo{Statistical definition from  \citep{GhezziEtAl2003} added}

@@

Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased:
Probability of failure-free operation of a computer program in a specified
environment for a specified time, i.e. the average time interval between two
failures also known as the mean time to failure (MTTF).
